Models of lens candidates from Space Warps CFHTLS

### 2017-03-03 parts/intro.tex
fix intro
last bugfixes, rearrange table and intro
work on intro

With no unambiguous dark-matter particle detections so far, dark
matter has studied only through its indirect consequences on galactic
and larger scales.  In most work, dark matter is taken to be a
collisionless non-relativistic fluid (cold dark matter or CDM); in
recent years, the ``millenium'' simulation by \cite{2005Natur.435..629S} has been
particularly influential in studying the formation of CDM structures.
Other scenarios have also been considered, such as a cold condensing
boson fluid \citep{2016ApJ...818...89S}.  There is a general
consensus, however, that the origins of galaxy lie in the
gravitational collapse, fragmentation, and mergers of dark-matter
clumps, into which fell gas, cooling through radiative processes to
form dense clouds and eventually stars.  There is, however, much
debate about the details, of which \cite{2012RAA....12..917S} provide
a nice summary.

Strong-lensing galaxies are a useful source of information on the
mutual dynamics and dark matter and gas in galaxies.  The topic has
been explored in several studies
\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires finding more lenses, of course, but also modelling their
masses.

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016A&A...592A..75P} and by visual inspection
by a citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
discovered an average of four lenses per square degree.  So one can be
optimistic about finding many thousands of lenses in the next
generation of wide-field surveys.  The expected flood of new lens
discoveries will need a similarly huge modelling effort to reconstruct
their mass distributions.  To prepare for the challenge of
massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
new modelling strategy, implemented as the SpaghettiLens system.  The
idea is to collaborate with experienced members of the citizen-science
community, who have already participated in lens discovery through
Space~Warps, as well as several other projects involving astronomical
data.

In this paper, we present SpaghettiLens models of lens-candidates
discovered through Space~Warps.  It's purpose is twofold: First, see if
plausible mass models can produce the overall configuration.  Second,
interpretation as lensing galaxies.

@@

\begin{itemize}
\item First we have diagnostics based on morphology of the
  system.
  Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
\begin{itemize}
\item The image morphology concisely described: double or quads,
  further sub-categorised to indicate the elongation direction of the
  lensing mass.
\item Whether the images are unblended.  Distinct unblended images are
  an advantage in modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible, in which case the modeller has to
  insert conjectural image positions.
\item Whether the lens is fairly isolated.
\end{itemize}
\item Second we have mass models, covered in Section~\ref{sec:massmodels}.
\begin{itemize}
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\item Whether the arrival-time surface and synthetic image are
  plausible.  In particular, additional images are implied in regions
  where they are not observed signal an unsatisfactory model.
  Figures~\ref{fig:arriv} and \ref{fig:synth} and \ref{fig:encl}.
\end{itemize}
\item Third, whether the implied lensing mass is plausible, given the
  star-light in the lensing galaxy.  Section~\ref{sec:stellar-mass}
  explains how we compare the lensing mass with the mass in stars in
  the lensing galaxy.  We estimate the stellar mass by comparing
  galaxy magnitudes from the CFHTLS pipeline with the well-known
  stellar-population models of \cite{2003MNRAS.344.1000B}.  We then
  extrapolate the stellar mass to a halo mass using the
  abundance-matching prescription of \cite{2010ApJ...710..903M}.
  Naturally, the lensing mass must be more than the stellar mass but
  no more than the total halo mass.  We then introduce what we call a
  halo index $\haloindex$ which gives an idea of how the lensing mass
  compares with these two bounds.  Figure~\ref{fig:stelmass}.
\end{itemize}

>>>>

With no unambiguous dark-matter particle detections so far, dark
matter has studied only through its indirect consequences on galactic
and larger scales.  In most work, dark matter is taken to be a
collisionless non-relativistic fluid (cold dark matter or CDM); in
recent years, the millenium simulation by \cite{2005Natur.435..629S} has been
particularly influential in studying the formation of CDM structures.
Other scenarios have also been considered, such as a cold condensing
boson fluid \citep{2016ApJ...818...89S}.  There is a general
consensus, however, that the origins of galaxy lie in the
gravitational collapse, fragmentation, and mergers of dark-matter
clumps, into which fell gas, cooling through radiative processes to
form dense clouds and eventually stars.  There is, however, much
debate about the details, of which \cite{2012RAA....12..917S} provide
a nice summary.

Strong-lensing galaxies are a useful source of information on the
mutual dynamics of dark matter and gas in galaxies.  The topic has
been explored in several studies
\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires finding more lenses, of course, but also modelling their
masses.

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016A&A...592A..75P} and by visual inspection
by citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
discovered an average of four lenses per square degree.  So one can be
optimistic about finding many thousands of lenses in the next
generation of wide-field surveys.  The expected flood of new lens
discoveries will need a similarly huge modelling effort to reconstruct
their mass distributions.  To prepare for the challenge of
massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
new modelling strategy, implemented as the SpaghettiLens system.  The
idea is to collaborate with experienced members of the citizen-science
community, who have already participated in lens discovery through
Space~Warps, as well as several other projects involving astronomical
data.

In this paper, we present SpaghettiLens models of lens-candidates discovered through Space~Warps.
It's purpose is twofold.
First to check if the created models look like plausible lenses and whether the shortcomings diagnosed in \cite{2015MNRAS.447.2170K} were fixed.
Second to introduce diagnostic criteria that help filter out the most probable lens candidates and the possibly most rewarding for future follow up observations.
While introducing these diagnostic criteria, we also gain some preliminary estimations of some properties of the lens-candidates as galaxies.

The analysis presented in this paper is somewhat limited by the fact that no source redshifts are available\footnote{Source redshifts were set to z=2 for all systems.} yet and that the redshifts of the lenses have large error bars.
Nevertheless it is interesting to see what trends we can observe with the already available data.
One should also keep in mind that the existing pipeline allows to replace those values with more precise ones as soon as they are available and rerun this analysis without any further work involved.

% It's purpose is twofold: First, to see if
% plausible mass models can produce the overall configuration.  Second, to
% check their interpretation as lensing galaxies.

@@

\begin{itemize}
\item First we have diagnostics based on morphology of the
  system.
  Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
\begin{itemize}
\item Whether the images are unblended.  Distinct unblended images are
  an advantage in modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible, in which case the modeller has to
  insert conjectural image positions.
\item Whether the lens is fairly isolated.
\item The image morphology concisely described: double or quads,
  further sub-categorised to indicate the elongation direction of the
  lensing mass.
\end{itemize}
\item Second we have mass models, covered in Section~\ref{sec:massmodels}.
\begin{itemize}
\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
\item Whether the arrival-time surface and synthetic image are
  plausible.  In particular, additional images are implied in regions
  where they are not observed signal an unsatisfactory model.
  Figures~\ref{fig:arriv} and \ref{fig:synth} and \ref{fig:encl}.
\end{itemize}
\item Third, whether the implied lensing mass is plausible, given the
  star-light in the lensing galaxy.  Section~\ref{sec:stellar-mass}
  explains how we compare the lensing mass with the mass in stars in
  the lensing galaxy.  We estimate the stellar mass by comparing
  galaxy magnitudes from the CFHTLS pipeline with the well-known
  stellar-population models of \cite{2003MNRAS.344.1000B}.  We then
  extrapolate the stellar mass to a halo mass using the
  abundance-matching prescription of \cite{2010ApJ...710..903M}.
  Naturally, the lensing mass must be more than the stellar mass but
  no more than the total halo mass.  We then introduce what we call a
  halo index $\haloindex$ which gives an idea of how the lensing mass
  compares with these two bounds.  Figure~\ref{fig:stelmass}.
\end{itemize}
